Water Management

### 2020-02-24 Paper/paper.tex
changes as discussed

\subsection{Dynamic Programming}

@@

\subsection{The Bellman Equation}

@@

So the value of the control variable to be set is the one that maximizes both the utility of the current state plus (recursively) the value $V$ of the next state $s'$ which is discounted by a factor of $\beta$. 
%TODO hier noch auf die Definition von beta eingehen? Was ist beta und warum ist das relevant?

\subsection{Computation of the value function}

@@

which equals to finding the column $aux$ that maximizes the expected value over all states.
We repeat this step over and over again until the our value function $V$ converges.
In our case the function converges, if the norm of the difference between $V'$ and $V$ falls below a certain tolerance value \\

% TODO Fehlen hier nicht noch ein paar Sätze dazu wie wir die optimal irrigation policy extrahieren?

@@

In edge cases one can find steady states as low as 3.5 or as high as 5.2. 
The curve resembles a normal distribution.

@@

We also looked at how changes in the discount factor $\beta$ influenced the optimal irrigation policy (Figure 7).

@@

We then went on and looked at the effect of increased rainfall volatility (Figures 9 and 10).

>>>>

\subsubsection{Dynamic Programming}

@@

\subsubsection{The Bellman Equation}

@@

So the value of the control variable to be set is the one that maximizes both the utility of the current state plus (recursively) the value $V$ of the next state $s'$ which is discounted by a factor of $\beta$. 
%TODO hier noch auf die Definition von beta eingehen? Was ist beta und warum ist das relevant?
\subsection{Implementation}
\subsubsection{Computation of the value function}

@@

which equals to finding the column $aux$ that maximizes the expected value over all states.
We repeat this step over and over again until the our value function $V$ converges.
In our case the function converges, if the norm of the difference between $V'$ and $V$ falls below a certain tolerance value \\
% TODO Fehlen hier nicht noch ein paar Sätze dazu wie wir die optimal irrigation policy extrahieren?

\subsubsection{TODO: Forward Simulation}

@@

The curve resembles a normal distribution with a standard deviation of $\sigma=0.37$.

@@

We also looked at how changes in the discount factor $\beta$ influenced the optimal irrigation policy (\ref{fig:optimal-irrigation-beta}).

@@

We then went on and looked at the effect of increased rainfall volatility (\ref{fig:aggregated-use-rainfall-default} and \ref{fig:aggregated-use-rainfall-more-volatile}).
